Contracts for unions and intersections are hard for Nickel

### 2021-05-28 paper.tex
Add a few lines to explain the syntax

\lstdefinelanguage{nickel}{
    keywords=[1]{
      if,
      then,
      else,
      switch,
    },
    keywords=[2]{
      let,
      rec,
      fun,
      in
    },
    keywords=[3]{
      Num,
      Bool,
      Str,
      List,
      Dyn,
      forall,
    },
    keywordsprefix=\#,
    keywords=[4]{
      true,
      false,
      null
    },
    keywords=[5]{
      doc,
      default,
    },
    sensitive=true, % keywords are case-sensitive
    morecomment=[l]{//}, % l is for line comment
    morecomment=**[is][\color{gray}]{\$}{\$},
    morestring=[b]", % defines that strings are enclosed in double quotes
    morestring=[s]{m\#"}{"\#m},
    moredelim=[is][\color{gray}]{\$}{\$},
    literate=
        *{->}{$\rightarrow$}1
        {=>}{$\Rightarrow$}1
        {>=}{$\geq$}1
        {<=}{$\leq$}1
} %

@@

>>>>

\lstdefinelanguage{nickel}{
    keywords=[1]{
      if,
      then,
      else,
      switch,
    },
    keywords=[2]{
      let,
      rec,
      fun,
      in
    },
    keywords=[3]{
      Num,
      Bool,
      Str,
      List,
      Dyn,
      forall,
    },
    keywordsprefix=\#,
    keywords=[4]{
      true,
      false,
      null
    },
    keywords=[5]{
      doc,
      default,
    },
    sensitive=true, % keywords are case-sensitive
    morecomment=[l]{//}, % l is for line comment
    morecomment=**[is][\color{gray}]{\$}{\$},
    morestring=[b]", % defines that strings are enclosed in double quotes
    morestring=[s]{m\#"}{"\#m},
    moredelim=[is][\color{gray}]{\$}{\$},
    literate=
        *{->}{$\rightarrow$}1
        {...}{\ldots}1
        {=>}{$\Rightarrow$}1
        {>=}{$\geq$}1
        {<=}{$\leq$}1
} %

@@

We will use the syntax of Nickel to write most examples throughout this paper.
Syntactically, Nickel looks like a simple ML language with records. \nickel{let
id = value in exp} is used to bind a value to an identifier in an expression.
Functions are declared using the \nickel{fun arg1 ... argn => body} syntax. List
are written as \nickel{[x1, ..., xn]} and records as \nickel{\{ field1 = value1,
..., fieldn = valuen \}}. Some examples uses constructions that are not
currently available in Nickel for illustration purpose: in particular, we will
use \nickel{A & B} (resp.  \nickel{A | B}) for the intersection (resp. union) of
contracts (or types) \nickel{A} and \nickel{B}.
